Associations between Chlorophyll *a* and various Microcystin-LR Health Advisory

### 2015-09-16 manuscript/manuscript.Rmd
fixed some rendering issues

```{r chla_micro_scatter, echo=FALSE, fig.width=7, fig.cap="Scatterplot showing association betweeen chlorophyll \\textit{a} and microcystin-LR. \\label{fig:chla_micro_scatter}"}
plot_scatter(nla_dat,xvar="log_chla",yvar = "log_micro",pt_col=viridis(1),
             x=expression(paste('Log10 Chl ', italic("a"),' (',mu,'g/L)')),
             y=expression(paste('Log10 microcystin-LR',' (',mu,'g/L)')))
```

@@

<!--
```{r chla_micro_cdf, echo=FALSE, fig.width=8, fig.cap="Conditional probability plots showing association between the probability of exceeding various microcystin-LR (MLR) health advisory Levels. \\label{fig:chla_micro_cdf}"}
plot_cdf(nla_dat[,c("log_chla","log_micro")],"")
```

@@

```{r epa_child_cp_plot, echo=FALSE, fig.width=7, fig.cap="Conditional probability plots showing association between the probability of exceeding various microcystin-LR (MLR) health advisory Levels. \\label{fig:multi_cp_plot}"}
multiplot(
  plot_cp(epa_child_cp,x = "Log 10 Chlorophyll", 
          y = "Probability of Exceeding 0.3 ug/L MLR",
          title="U.S. EPA Children's Drinking Water Advisory Level"),
  plot_cp(who_drink_cp, x = "Log 10 Chlorophyll", 
          y = "Probability of Exceeding 1 ug/L MLR", 
          title="WHO Drinking Water Advisory Level"),
  plot_cp(epa_adult_cp, x = "Log 10 Chlorophyll", 
          y = "Probability of Exceeding 1.6 ug/L MLR", 
          title="U.S. EPA Adult Drinking Water Advisory Level"),
  plot_cp(who_rec_low1_cp, x = "Log 10 Chlorophyll", 
          y = "Probability of Exceeding 2 ug/L MLR", 
          title="WHO Recreational Water Advisory Level"),
  cols=1
)
```

>>>>

```{r chla_micro_scatter, echo=FALSE, fig.width=6, fig.cap="Scatterplot showing association betweeen chlorophyll \\textit{a} and microcystin-LR. \\label{fig:chla_micro_scatter}"}
plot_scatter(nla_dat,xvar="log_chla",yvar = "log_micro",pt_col=viridis(1),
             x=expression(paste('Log10 Chl ', italic("a"),' (',mu,'g/L)')),
             y=expression(paste('Log10 microcystin-LR',' (',mu,'g/L)')))
```

@@

<!--
```{r chla_micro_cdf, echo=FALSE, fig.cap="Conditional probability plots showing association between the probability of exceeding various microcystin-LR (MLR) health advisory Levels. \\label{fig:chla_micro_cdf}"}
plot_cdf(nla_dat[,c("log_chla","log_micro")],"")
```

@@

```{r epa_child_cp_plot, echo=FALSE, fig.width=6, fig.cap="Conditional probability plots showing association between the probability of exceeding various microcystin-LR (MLR) health advisory Levels. A.) Plot for U.S. EPA childrens drinking water advisory (0.3 $\\mu$g/L). B.) Plot for WHO drinking water advisory (1 $\\mu$g/L). C.) Plot for U.S. EPA adult drinking water advisory (1.6 $\\mu$g/L). D.) Plot for WHO recreational advisory (2 $\\mu$g/L). \\label{fig:multi_cp_plot}"}
multiplot(
  plot_cp(epa_child_cp,x = "Log 10 Chlorophyll", 
          y = "Conditional Probability",
          title="A."),
  plot_cp(who_drink_cp, x = "Log 10 Chlorophyll", 
          y = "Conditional Probability", 
          title="B."),
  plot_cp(epa_adult_cp, x = "Log 10 Chlorophyll", 
          y = "Conditional Probability", 
          title="C."),
  plot_cp(who_rec_low1_cp, x = "Log 10 Chlorophyll", 
          y = "Conditional Probability", 
          title="D."),
  cols=2
)
```
